Q-compensated denoising of seismic data

### 2022-01-15 qcomp/paper.tex
fix qcomp

\title{Q-compensated denoising of seismic data}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Hang Wang, Guangtan Huang, Yangkang Chen, and Wei Chen
\thanks{H. Wang, G. Huang, Y. Chen are with Zhejiang University.}
\thanks{W. Chen is with Yangtze University (corresponding author).}
\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140).}}
\maketitle

@@

\begin{keywords}
Q-compensation, denoising, and seismic data
\end{keywords}

\section{Introduction}
Recovering the seismic signals from the strong background seismic noise, also known as seismic denoising, is of great importance of the whole seismic data processing chain \cite{yanan2014,yanhui2016,amir2017ieee,li2018multidimensional,wang2019hankel}.  There have been a lot of classic denoising algorithms in the literature, e.g., the prediction-based denoising methods \cite{canales1984,abma1995}, \new{the sparse transform based denoising methods \cite{fomel2010seislet,mostafa2016geo,mostafa2016bssa,mousavi2017automatic}}, the mode decomposition based denoising methods \cite{chenwei2012}, the rank-reduction based denoising methods \cite{mssa,weilin2016dmssa,zhaoqiang2019tgrs}, etc. Despite \old{of }the reported success in the field of seismic denoising, the traditional methods cannot resolve the problem of amplitude loss due to the anelastic attenuation when seismic waves are propagated in subsurface media. \new{The amplitude loss could make the recorded seismic data contain very weak events.} This limitation makes all traditional seismic denoising methods fail in dealing with highly attenuated seismic data, e.g., the weak seismic signals. What is worse is that due to the weak energy of those attenuated seismic events, the spatial correlation is also mitigated, thereby causing a high probability in damaging the weak events during the denoising process. \new{Besides, most denoising methods also affect the amplitude, thus causing a high chance that the attenuation estimation using denoised signal results in overestimation of the quality factor, Q.} In this paper, we will focus on the challenging problem of simultaneous denoising and attenuation compensation (Q-compensation). The goal is to develop an inversion framework that \old{can }not only \new{can} attenuate the random noise, but also compensate for the anelastic amplitude loss and thus increase the vertical resolution.

The anelastic attenuation is usually described by the quality factor (Q). Kjartansson (1979) \cite{kjartansson1979constant} proposed a constant Q-model, which describes an attenuation medium \cite{bickel1985plane,wang2002stable,shen2018q,shen2018q2}. In the constant Q-model, the quality factor does not vary with frequency \cite{braginsky1989quality,dai2012multi}. The estimation of Q is important in a variety of geophysical inverse problems, e.g., Q-compensated seismic migration, high-fidelity seismic interpretation, reservoir fluid characterization, and seismic risk estimation \cite{mousavi2014jgr,shank2018image,cheng2018q,jyothi2017seismic,luo2019q,chen2019multichannel}. Q-compensation, a widely used method to seismic imaging, is becoming a \old{heated}\new{hot} researching topic in exploration geophysics \cite{guo2017adjoint,zhou2019viscoacoustic,aharchaou2019prestack}. \new{Besides, Q can also be used to interpret the large-scale geological features \cite{zhao2018lateral}.}

Reverse time migration (RTM) is thought as one of the most effective seismic imaging methods \cite{baysal1983reverse,yoon2004challenges,dai2012multi}. In recent years, Q-compensation research for different forms of reverse time migration has emerged. \cite{zhang2010compensating} proposed a Q-compensated RTM, where a \old{viscoelastic}\new{viscoacoustic} wave equation is used for compensating amplitude attenuation and phase dispersion effects.  Researchers also used the separated fractional Laplace equation to approximate the constant-Q wave equation for viscous acoustic medium modeling and imaging tasks \cite{zhu2014q,fathalian2020approach}, which plays an important role in effectively using constant-Q in data processing \cite{harris2014q,wang2018adaptive}.\old{ The viscoelastic least-square inverse time migration (also known as Q-LSRTM) is a linear inversion of \new{a} subsurface reflectance model from lossy data ?. Compared with the traditional migration method, it could compensate for the amplitude loss of the migration image caused by the strong underground attenuation, and can produce the reflector accurately located at the depth. Researchers have developed different algorithms and demonstrate the Q-LSRTM method converges significantly faster than least-square reserve time migration ?.} Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2018accelerating}. \old{By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model ?. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} ? proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate ?.}

%Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite{xue2017visco,xue2018accelerating}. By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model \cite{alasmri2019towards,li2016application,xue2016q,wang2019q}. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} \cite{xin20093} proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate \cite{harris2014q,he2012q,xin2014robust}.

@@

\subsection{Convolution model with anelastic attenuation}
The convolution model is well known as:
\begin{equation}
\label{eq:conv}
\mathbf{d} = \mathbf{Wr},
\end{equation}
where $\mathbf{d}$ denotes the seismic data, $\mathbf{W}$ denotes the convolution matrix that is composed of the source wavelet $\mathbf{w}$, and $\mathbf{r}$ denotes the reflectivity. When considering the subsurface seismic anelastic attenuation, the convolution model \ref{eq:conv} can be modified as:
\begin{equation}
\label{eq:conva}
\mathbf{d} = \mathbf{WAr},
\end{equation}
where $\mathbf{A}$ denotes the attenuation operator. In an integral form, equation \ref{eq:conva} can be expressed as \cite{margrave2011gabor,yufeng2018l12}:
\begin{equation}
\label{eq:int}
d(\omega) = w(\omega) \int r(t)a(\omega,t)e^{-i\omega t}dt,
\end{equation}
where $d(\omega)$ and $w(\omega)$ denote the spectrum of the seismic data $d(t)$ and wavelet function $w(t)$ in the frequency domain, respectively. $a(\omega,t)$ corresponds to an attenuation function. $r(t)$ is the reflectivity function in the time domain. The attenuation function can be defined based on the constant-Q theory as follows \cite{zhu2014q,yufeng2018l12}:
\begin{equation}
\label{eq:af}
a(\omega, t) = e^{-\frac{\omega t}{2Q}\left | \frac{\omega}{\omega_h} \right |^{-\gamma}}e^{i \omega t \left | \frac{\omega}{\omega_h} \right |^{-\gamma}},
\end{equation}
where $\gamma=\frac{1}{\pi Q}$, and $\omega_h$ is a reference frequency \new{e.g., 30 Hz}.

@@

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dc}
   \label{fig:syn-dc}}\\
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da}
   \label{fig:syn-da}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn}
   \label{fig:syn-dn}}
  \caption{Synthetic data example. \old{(a) Clean data. (b) Noisy data with attenuated amplitude. (c) Enhanced data using fx method. (d) Enhanced data using the proposed method.}\new{(a) Clean data. (b) Clean data with attenuated amplitude. (c) Noisy data with attenuated amplitude.}}
  \label{fig:syn-dc,syn-da,syn-dn}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2}
   \label{fig:syn-d2}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1}
   \label{fig:syn-d1}}
  \caption{Synthetic data example. (a) Denoised data using FX method. (d) Q-compensated and denoised data using the proposed method.}
  \label{fig:syn-d2,syn-d1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da-simi}
   \label{fig:syn-da-simi}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn-simi}
   \label{fig:syn-dn-simi}}\\
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2-simi}
   \label{fig:syn-d2-simi}}
 \subfigure[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1-simi}
   \label{fig:syn-d1-simi}}
  \caption{Similarity comparison between the target data and the ground truth for (a) attenuated data, (b) noisy data, (c) denoised data using FX method, and (d) the proposed method.}
  \label{fig:syn-da-simi,syn-dn-simi,syn-d2-simi,syn-d1-simi}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss0}
   \label{fig:syn-ss0}}
 \subfigure[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss-z}
   \label{fig:syn-ss-z}}
  \caption{Trace-by-trace (3rd trace in Figs. \ref{fig:syn-dc,syn-da,syn-dn} and \ref{fig:syn-d2,syn-d1}) comparison for the synthetic data example, in the original scale (a), and in the zoomed scale (b). The red line denotes the clean attenuated data. The pink line corresponds to the noisy attenuated data. The green line corresponds to the Q-compensated denoising method. The blue line corresponds to the FX method.  The black line corresponds to the ground truth. It is clear that the black and green lines are close to each other.}
  \label{fig:syn-ss0,syn-ss-z}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-0}
   \label{fig:real-dn-0}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-0}
   \label{fig:real-d2-0}}
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-0}
   \label{fig:real-d1-0}}   
  \caption{Field data example. (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-0,real-d2-0,real-d1-0}
\end{figure}

@@

Note that 
\begin{equation}
\label{eq:l1l2}
\parallel \mathbf{r} \parallel_1 = \sum_{i} |r_i| =  \sum_{i} |r_i| |r_i|^{-1} |r_i| = \parallel \mathbf{W}_r\mathbf{r} \parallel_2^2,
\end{equation}
where $[\mathbf{W}_r]_{ii}=|r_i|^{-1/2}$. To avoid the singularity caused by too small $r_i$, a threshold needs to be defined \cite{amr2014}.

@@

Equation \ref{eq:cost2} can be solved via the classic conjugate gradient method. In summary, when solving equation \ref{eq:cost1}, we need to iteratively solve for $\mathbf{m}$ and $\mathbf{W}_r$. $\mathbf{W}_r$ needs to be re-calculated during the iterations. \new{Following Daniel (2003) \cite{daniel2003}}, we ease the inconvenience in selecting the balancing parameter $\lambda$ by adjusting the sparsity constraint through the number of re-weighting iterations. A higher number of re-weighting iterations corresponds to a higher trade-off parameter $\lambda$ and vice versa. The detailed preconditioned conjugate gradient algorithm to solve equation \ref{eq:cost1} is provided in Algorithm \ref{alg:alg1}, where the input are the forward operator $\mathbf{F}$, raw data $\mathbf{d}$, and initial guess of $\mathbf{m}_0$, inner and outer iterations $N_i$ and $N_o$. When the  reflectivity $\hat{\mathbf{r}}=\mathbf{r}_{N_i}$ is solved through algorithm \ref{alg:alg1}, the Q-compensated and denoised data can be obtained by $\hat{\mathbf{s}} = \mathbf{W}\hat{\mathbf{r}}$.

@@

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z1}
   \label{fig:real-dn-z1}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z1}
   \label{fig:real-d2-z1}}
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z1}
   \label{fig:real-d1-z1}}   
  \caption{Zoomed comparison for the field data example (corresponding to the pink boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-z1,real-d2-z1,real-d1-z1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z2}
   \label{fig:real-dn-z2}}\\
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z2}
   \label{fig:real-d2-z2}} 
 \subfigure[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z2}
   \label{fig:real-d1-z2}}   
  \caption{Zoomed comparison for the field data example (corresponding to the red boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method (Q=50).}
  \label{fig:real-dn-z2,real-d2-z2,real-d1-z2}
\end{figure}

\begin{figure*}[ht!]
 \centering
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-0}
   \label{fig:real-d1-q60-0}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-0}
   \label{fig:real-d1-q70-0}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-0}
   \label{fig:real-d1-q80-0}}  \\
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-0}
   \label{fig:real-d1-q90-0}}
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-0}
   \label{fig:real-d1-q100-0}}   
 \subfigure[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-0}
   \label{fig:real-d1-q120-0}}   
  \caption{Field data example with different Q. (a) Q=60. (b) Q=70. (c) Q=80. (d) Q=90. (e) Q=100. (f) Q=120. The areas highlighted by the frame boxes is zoomed in Fig. \ref{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}.}
  \label{fig:real-d1-q60-0,real-d1-q70-0,real-d1-q80-0,real-d1-q90-0,real-d1-q100-0,real-d1-q120-0}
\end{figure*}

>>>>

\title{Q-compensated denoising of seismic data}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Hang Wang, Guangtan Huang, Yangkang Chen, and Wei Chen}
%\thanks{H. Wang, G. Huang, Y. Chen are with Zhejiang University.}
%\thanks{W. Chen is with Yangtze University (corresponding author).}
%\thanks{The research is supported by the National Natural Science Foundation of China (Grant No. 41804140).}}
\maketitle

@@

%\begin{keywords}
%Q-compensation, denoising, and seismic data
%\end{keywords}

\section{Introduction}
Recovering the seismic signals from the strong background seismic noise, also known as seismic denoising, is of great importance of the whole seismic data processing chain \cite[]{yanan2014,yanhui2016,amir2017ieee,li2018multidimensional,wang2019hankel}.  There have been a lot of classic denoising algorithms in the literature, e.g., the prediction-based denoising methods \cite[]{canales1984,abma1995}, \new{the sparse transform based denoising methods \cite[]{fomel2010seislet,mostafa2016geo,mostafa2016bssa,mousavi2017automatic}}, the mode decomposition based denoising methods \cite[]{chenwei2012}, the rank-reduction based denoising methods \cite[]{mssa,weilin2016dmssa,zhaoqiang2019tgrs}, etc. Despite \old{of }the reported success in the field of seismic denoising, the traditional methods cannot resolve the problem of amplitude loss due to the anelastic attenuation when seismic waves are propagated in subsurface media. \new{The amplitude loss could make the recorded seismic data contain very weak events.} This limitation makes all traditional seismic denoising methods fail in dealing with highly attenuated seismic data, e.g., the weak seismic signals. What is worse is that due to the weak energy of those attenuated seismic events, the spatial correlation is also mitigated, thereby causing a high probability in damaging the weak events during the denoising process. \new{Besides, most denoising methods also affect the amplitude, thus causing a high chance that the attenuation estimation using denoised signal results in overestimation of the quality factor, Q.} In this paper, we will focus on the challenging problem of simultaneous denoising and attenuation compensation (Q-compensation). The goal is to develop an inversion framework that \old{can }not only \new{can} attenuate the random noise, but also compensate for the anelastic amplitude loss and thus increase the vertical resolution.

The anelastic attenuation is usually described by the quality factor (Q). Kjartansson (1979) \cite[]{kjartansson1979constant} proposed a constant Q-model, which describes an attenuation medium \cite[]{bickel1985plane,wang2002stable,shen2018q,shen2018q2}. In the constant Q-model, the quality factor does not vary with frequency \cite[]{braginsky1989quality,dai2012multi}. The estimation of Q is important in a variety of geophysical inverse problems, e.g., Q-compensated seismic migration, high-fidelity seismic interpretation, reservoir fluid characterization, and seismic risk estimation \cite[]{mousavi2014jgr,shank2018image,cheng2018q,jyothi2017seismic,luo2019q,chen2019multichannel}. Q-compensation, a widely used method to seismic imaging, is becoming a \old{heated}\new{hot} researching topic in exploration geophysics \cite[]{guo2017adjoint,zhou2019viscoacoustic,aharchaou2019prestack}. \new{Besides, Q can also be used to interpret the large-scale geological features \cite[]{zhao2018lateral}.}

Reverse time migration (RTM) is thought as one of the most effective seismic imaging methods \cite[]{baysal1983reverse,yoon2004challenges,dai2012multi}. In recent years, Q-compensation research for different forms of reverse time migration has emerged. \cite[]{zhang2010compensating} proposed a Q-compensated RTM, where a \old{viscoelastic}\new{viscoacoustic} wave equation is used for compensating amplitude attenuation and phase dispersion effects.  Researchers also used the separated fractional Laplace equation to approximate the constant-Q wave equation for viscous acoustic medium modeling and imaging tasks \cite[]{zhu2014q,fathalian2020approach}, which plays an important role in effectively using constant-Q in data processing \cite[]{harris2014q,wang2018adaptive}.\old{ The viscoelastic least-square inverse time migration (also known as Q-LSRTM) is a linear inversion of \new{a} subsurface reflectance model from lossy data ?. Compared with the traditional migration method, it could compensate for the amplitude loss of the migration image caused by the strong underground attenuation, and can produce the reflector accurately located at the depth. Researchers have developed different algorithms and demonstrate the Q-LSRTM method converges significantly faster than least-square reserve time migration ?.} Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite[]{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite[]{xue2018accelerating}. \old{By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model ?. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} ? proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate ?.}

%Q-compensation can be utilized in full waveform inversion (FWI) as well. FWI provides a reliable method for the establishment of \new{a} high-resolution underground model, especially for the construction of \new{a} complex geological structure model, which has been \old{fully}\new{extensively} studied\old{ and developed} in the past decades \cite[]{tarantola2005inverse,virieux2009overview}. Q-compensated FWI has been proved to be highly effective \new{for building a reliable subsurface velocity model} \cite[]{xue2017visco,xue2018accelerating}. By comparing the convergence rates of FWI with Q-compensated gradient and without Q-compensated gradient, we can know that the Q-compensation strategy can obviously improve the convergence of FWI, which is helpful for the fast inversion of \new{the} deep structure of velocity model \cite[]{alasmri2019towards,li2016application,xue2016q,wang2019q}. \old{However, attenuation reconstruction is always an ill-posed problem. Because the reliability of attenuation reconstruction depends on the precision of \new{the} initial velocity model to a great extent, FWI has the advantages of being more robust and stable, but the calculation cost is very high ?.} \cite[]{xin20093} proposed a ray based Q-tomography, which can be incorporated into the traditional depth velocity modeling process. In order to compensate for the attenuation in RTM and FWI imaging, it is necessary to estimate the spatial change rate of attenuation from the dataset. Q-tomography based on frequency shift data is very useful in estimating the uniform attenuation rate \cite[]{harris2014q,he2012q,xin2014robust}.

@@

\subsection{Convolution model with anelastic attenuation}
The convolution model is well known as:
\begin{equation}
\label{eq:conv}
\mathbf{d} = \mathbf{Wr},
\end{equation}
where $\mathbf{d}$ denotes the seismic data, $\mathbf{W}$ denotes the convolution matrix that is composed of the source wavelet $\mathbf{w}$, and $\mathbf{r}$ denotes the reflectivity. When considering the subsurface seismic anelastic attenuation, the convolution model \ref{eq:conv} can be modified as:
\begin{equation}
\label{eq:conva}
\mathbf{d} = \mathbf{WAr},
\end{equation}
where $\mathbf{A}$ denotes the attenuation operator. In an integral form, equation \ref{eq:conva} can be expressed as \cite[]{margrave2011gabor,yufeng2018l12}:
\begin{equation}
\label{eq:int}
d(\omega) = w(\omega) \int r(t)a(\omega,t)e^{-i\omega t}dt,
\end{equation}
where $d(\omega)$ and $w(\omega)$ denote the spectrum of the seismic data $d(t)$ and wavelet function $w(t)$ in the frequency domain, respectively. $a(\omega,t)$ corresponds to an attenuation function. $r(t)$ is the reflectivity function in the time domain. The attenuation function can be defined based on the constant-Q theory as follows \cite[]{zhu2014q,yufeng2018l12}:
\begin{equation}
\label{eq:af}
a(\omega, t) = e^{-\frac{\omega t}{2Q}\left | \frac{\omega}{\omega_h} \right |^{-\gamma}}e^{i \omega t \left | \frac{\omega}{\omega_h} \right |^{-\gamma}},
\end{equation}
where $\gamma=\frac{1}{\pi Q}$, and $\omega_h$ is a reference frequency \new{e.g., 30 Hz}.

@@

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dc}
   \label{fig:syn-dc}}\\
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da}
   \label{fig:syn-da}}
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn}
   \label{fig:syn-dn}}
  \caption{Synthetic data example. \old{(a) Clean data. (b) Noisy data with attenuated amplitude. (c) Enhanced data using fx method. (d) Enhanced data using the proposed method.}\new{(a) Clean data. (b) Clean data with attenuated amplitude. (c) Noisy data with attenuated amplitude.}}
  \label{fig:syn-dc,syn-da,syn-dn}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2}
   \label{fig:syn-d2}}
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1}
   \label{fig:syn-d1}}
  \caption{Synthetic data example. (a) Denoised data using FX method. (d) Q-compensated and denoised data using the proposed method.}
  \label{fig:syn-d2,syn-d1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-da-simi}
   \label{fig:syn-da-simi}}
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-dn-simi}
   \label{fig:syn-dn-simi}}\\
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d2-simi}
   \label{fig:syn-d2-simi}}
 \subfloat[]{\includegraphics[width=0.22\textwidth]{synth/Fig/syn-d1-simi}
   \label{fig:syn-d1-simi}}
  \caption{Similarity comparison between the target data and the ground truth for (a) attenuated data, (b) noisy data, (c) denoised data using FX method, and (d) the proposed method.}
  \label{fig:syn-da-simi,syn-dn-simi,syn-d2-simi,syn-d1-simi}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss0}
   \label{fig:syn-ss0}}
 \subfloat[]{\includegraphics[width=0.5\textwidth]{synth/Fig/syn-ss-z}
   \label{fig:syn-ss-z}}
  \caption{Trace-by-trace (3rd trace in Figs. \ref{fig:syn-dc,syn-da,syn-dn} and \ref{fig:syn-d2,syn-d1}) comparison for the synthetic data example, in the original scale (a), and in the zoomed scale (b). The red line denotes the clean attenuated data. The pink line corresponds to the noisy attenuated data. The green line corresponds to the Q-compensated denoising method. The blue line corresponds to the FX method.  The black line corresponds to the ground truth. It is clear that the black and green lines are close to each other.}
  \label{fig:syn-ss0,syn-ss-z}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-0}
   \label{fig:real-dn-0}}\\
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-0}
   \label{fig:real-d2-0}}
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-0}
   \label{fig:real-d1-0}}   
  \caption{Field data example. (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-0,real-d2-0,real-d1-0}
\end{figure}

@@

Note that 
\begin{equation}
\label{eq:l1l2}
\parallel \mathbf{r} \parallel_1 = \sum_{i} |r_i| =  \sum_{i} |r_i| |r_i|^{-1} |r_i| = \parallel \mathbf{W}_r\mathbf{r} \parallel_2^2,
\end{equation}
where $[\mathbf{W}_r]_{ii}=|r_i|^{-1/2}$. To avoid the singularity caused by too small $r_i$, a threshold needs to be defined \cite[]{amr2014}.

@@

Equation \ref{eq:cost2} can be solved via the classic conjugate gradient method. In summary, when solving equation \ref{eq:cost1}, we need to iteratively solve for $\mathbf{m}$ and $\mathbf{W}_r$. $\mathbf{W}_r$ needs to be re-calculated during the iterations. \new{Following Daniel (2003) \cite[]{daniel2003}}, we ease the inconvenience in selecting the balancing parameter $\lambda$ by adjusting the sparsity constraint through the number of re-weighting iterations. A higher number of re-weighting iterations corresponds to a higher trade-off parameter $\lambda$ and vice versa. The detailed preconditioned conjugate gradient algorithm to solve equation \ref{eq:cost1} is provided in Algorithm \ref{alg:alg1}, where the input are the forward operator $\mathbf{F}$, raw data $\mathbf{d}$, and initial guess of $\mathbf{m}_0$, inner and outer iterations $N_i$ and $N_o$. When the  reflectivity $\hat{\mathbf{r}}=\mathbf{r}_{N_i}$ is solved through algorithm \ref{alg:alg1}, the Q-compensated and denoised data can be obtained by $\hat{\mathbf{s}} = \mathbf{W}\hat{\mathbf{r}}$.

@@

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z1}
   \label{fig:real-dn-z1}}\\
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z1}
   \label{fig:real-d2-z1}}
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z1}
   \label{fig:real-d1-z1}}   
  \caption{Zoomed comparison for the field data example (corresponding to the pink boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method.}
  \label{fig:real-dn-z1,real-d2-z1,real-d1-z1}
\end{figure}

\begin{figure}[htb!]
 \centering
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-dn-z2}
   \label{fig:real-dn-z2}}\\
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d2-z2}
   \label{fig:real-d2-z2}} 
 \subfloat[]{\includegraphics[width=0.23\textwidth]{field/Fig/real-d1-z2}
   \label{fig:real-d1-z2}}   
  \caption{Zoomed comparison for the field data example (corresponding to the red boxes in Fig. \ref{fig:real-dn-0,real-d2-0,real-d1-0}). (a) Raw data. (b) Enhanced data using fx method. (c) Enhanced data using the proposed method (Q=50).}
  \label{fig:real-dn-z2,real-d2-z2,real-d1-z2}
\end{figure}

\begin{figure*}[ht!]
 \centering
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-0}
   \label{fig:real-d1-q60-0}}
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-0}
   \label{fig:real-d1-q70-0}}   
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-0}
   \label{fig:real-d1-q80-0}}  \\
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-0}
   \label{fig:real-d1-q90-0}}
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-0}
   \label{fig:real-d1-q100-0}}   
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-0}
   \label{fig:real-d1-q120-0}}   
  \caption{Field data example with different Q. (a) Q=60. (b) Q=70. (c) Q=80. (d) Q=90. (e) Q=100. (f) Q=120. The areas highlighted by the frame boxes is zoomed in Fig. \ref{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}.}
  \label{fig:real-d1-q60-0,real-d1-q70-0,real-d1-q80-0,real-d1-q90-0,real-d1-q100-0,real-d1-q120-0}
\end{figure*}

\begin{figure*}[ht!]
 \centering
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q60-z1}
   \label{fig:real-d1-q60-z1}}
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q70-z1}
   \label{fig:real-d1-q70-z1}}   
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q80-z1}
   \label{fig:real-d1-q80-z1}}  \\
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q90-z1}
   \label{fig:real-d1-q90-z1}}
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q100-z1}
   \label{fig:real-d1-q100-z1}}   
 \subfloat[]{\includegraphics[width=0.3\textwidth]{field/Fig/real-d1-q120-z1}
   \label{fig:real-d1-q120-z1}}   
  \caption{Zoomed comparison of the field data example with different Q. (a) Q=60. (b) Q=70. (c) Q=80. (d) Q=90. (e) Q=100. (f) Q=120.}
  \label{fig:real-d1-q60-z1,real-d1-q70-z1,real-d1-q80-z1,real-d1-q90-z1,real-d1-q100-z1,real-d1-q120-z1}
\end{figure*}
